Anisotropic in-plane thermal conductivity observed in multilayer silicene

### 2017-10-29 latex/paper.tex
修改文章

% @Author: YangZhou
% @Date:   2017-06-20 20:27:38
% @Last Modified by:   YangZhou
% @Last Modified time: 2017-10-23 21:19:00
\documentclass[%
 reprint,
 amsmath,amssymb,
 aps,
 prb,
]{revtex4-1}
\preprint{APS/123-QED}
\usepackage{graphicx}% Include figure filesxx
\usepackage{bm}% bold math
\newcommand{\angstrom}{\mbox{\normalfont\AA}}
\begin{document}
\title{Anisotropic in-plane thermal conductivity observed in multilayer silicene}
\author{Yang Zhou${}^{1,3}$}
\author{Chao-Yu Chen${}^{2}$}
\author{Zhi-Xin Guo${}^{2}$}
\email{zxguo08@hotmail.com}
\author{Shi-You Chen${}^{1}$}
\author{Hong-Jun Xiang${}^{1}$}
\author{Xin-Gao Gong${}^{1,3}$}
\email{xggong@fudan.edu.cn}
\affiliation{
  ${}^1$Key Laboratory for Computational Physical Science (Ministry of Education), State Key Laboratory of Surface Physics and Department of Physics, Fudan University, Shanghai 200433, China\\
  ${}^2$Department of Physics, Xiangtan University, Xiangtan 411105, China\\
  ${}^3$Collaborative Innovation Center of Advanced Microstructures, Nanjing 210093, Jiangsu, China
}
\begin{abstract}
  By means of non-equilibrium molecular dynamics simulation, we systematically study the thermal transportation properties of different types of multilayer silicon. It is found that the thermal transport properties of multilayer silicon structures have significant surface effect and size effect in thickness direction. Surface reconstruction affects heat transport very well , the thermal conductivity of bilayer silicon with different reconstruction can reach up to $11.6 W/mK$, and can be as low as $1.2 W/mK$ and the anisotropy can be as high as $57.3\%$.With the increase of the number of layers, the thermal conductivity of the zigzag direction changed little, but the thermal conductivity increased significantly in the armchair direction, and the anisotropy of thermal conductivity decreased which is due to the smaller affection in more layer structure. This work could be helpful in the field of heat management, thermoelectric applications involving silicon and other multilayer nano materials in the future.
  \begin{description}
    \item[Keywords]
          Thermal conductivity, multilayer silicon, surface reconstruction, anisotropy
  \end{description}
\end{abstract}

@@

In this paper, based on the large scale parallel and efficient LAMMPS molecular dynamics software package\cite{Parks2007}, we study the thermal conductivity of multilayer silicon structure by using the non-equilibrium temperature gradient method. Because of the abundant silicon structure model, the phase reconstruction has attracted much attention. In order to well simulate the structures of different phase by MD, the latest Mod potential is chosen\cite{Kumagai2007Development}, which is able to reconstruct the silicon material elastic constants, the melting point and phase transition. Firstly, we use conjugate gradient method to optimize these structures. All structures are shown in FIG.\ref{fig:structures}.

@@

\begin{table*}
  \caption{\label{tab:table1}
    Symmetry of the structures, binding energy $E_c(eV/Si)$ and structure features}
  \begin{ruledtabular}
    \begin{tabular}{cccccccc}
      Name
           & Minimal period
           & Symmetry
           & $E_c$ in Guo
           & $E_c$ in MD
           & Buckling Feature                                                                       \\
      \hline
      2l1  & $1 \times 1$             & Cmme    & 5.000 & 4.145 & Smooth                            \\
      2l2  & $\sqrt{2}\times\sqrt{2}$ & C12/m1  & 4.991 & 4.204 & Large buckling and symmetric      \\
      2l3  & $2 \times 2$             & C12/m1  & 5.063 & 4.257 & Large buckling and tilt symmetric \\
      2lh  & $2 \times 2$             & P1      & 5.073 & 4.216 & Large buckling                    \\
      2lr3 & $\sqrt{3}\times\sqrt{3}$ & P1      & -     & 4.225 & Small buckling and symmetric      \\
      3l1  & $2 \times 1$             & P121/m1 & 5.138 & 4.337 & -                                 \\
      3l2  & $2 \times 1$             & P1      & 5.135 & 4.298 & -                                 \\
      4l1  & $2 \times 1$             & P1      & 5.225 & 4.368 & -                                 \\
      2l2  & $\sqrt{2}\times\sqrt{2}$ & C12/m1  & 4.991 & 4.204 & Large buckling and symmetric      \\
      2l3  & $2 \times 2$             & C12/m1  & 5.063 & 4.257 & Large buckling and tilt symmetric \\
      2lh  & $2 \times 2$             & P1      & 5.073 & 4.216 & Large buckling                    \\
      2lr3 & $\sqrt{3}\times\sqrt{3}$ & P1      & -     & 4.225 & Small buckling and symmetric      \\
      3l1  & $2 \times 1$             & P121/m1 & 5.138 & 4.337 & -                                 \\
      3l2  & $2 \times 1$             & P1      & 5.135 & 4.298 & -                                 \\
      4l1  & $2 \times 1$             & P1      & 5.225 & 4.368 & -                                 \\
    \end{tabular}
  \end{ruledtabular}

\end{table*}

@@

We firstly investigate the effect of surface reconstruction on thermal conductivity. 5 kinds of silicon structures of armchair and zigzag were selected to study. The relationship between the thermal conductivity and the length of bilayer silicon in different directions is shown in FIG.\ref{fig:2l_length}. the thermal conductivity of 2l1 structure increases with the length the most significantly, followed by the 2l3 structure and 2lr3 structure, while the least significant is the structure of 2l2 and 2lh. In addition, the structure with the thermal conductivity increasing significantly with the length is obviously anisotropy, different from single layer silicon and bulk silicon, who tend to be isotropic. In the aspect of structural, smooth 2l1 is most favorable for heat conduction, while 2l2 structure whose surface is made of a highly symmetrical and highly buckling pentacyclic ring "bird cage" is most unfavorable for thermal conductivity but suitable for thermoelectric materials. And the edges of the two directions are similar in shape, leading to small difference of heat transport.

\begin{figure}[b]
  \includegraphics[width=0.48\textwidth]{images/2l_length}
  \caption{\label{fig:2l_length} (color online) The thermal conductivity dependence on length for five types of bilayer silicon. The scatters are the results of MD simulations while the lines are fitted with Eq.\ref{eq_nemd}. The letter z/a in the legend mean the transport direction is zigzag/armchair.}
\end{figure}

\begin{figure}[b]
  \includegraphics[width=0.48\textwidth]{images/vl_length}
  \caption{\label{fig:vl_length}(color online) The dependence on length of thermal conductivity for silicon with variable layers.}
\end{figure}

@@

\begin{table*}
  \caption{\label{tab:table2}
    The thermal conductivity and anisotropic ratio of different multi-layer silicene.Along with the average heat capacity ($kJ/m^3/K$) of zigzag direction and armchair direction.}
  \begin{ruledtabular}
    \begin{tabular}{cccccccccccc}
            & $\kappa_{z,\infty}$
            & $\kappa_{a,\infty}$
            & $\chi$
            & $Cv_{z}$
            & $Cv_{a}$
            &
            & $\kappa_{z,\infty}$
            & $\kappa_{a,\infty}$
            & $\chi$
            & $Cv_{z}$
            & $Cv_{a}$                                                                                              \\
      \hline
      2l1   & 11.6                & 6.5  & 43.9\% & 165.8 & 166.7 & 2l2      & 1.5  & 1.2  & 20.0\% & 38.44 & 38.44 \\
      2l3   & 5.0                 & 9.7  & 48.5\% & 23.38 & 23.38 & 2lr3     & 8.2  & 3.5  & 57.3\% & 10.15 & 10.15 \\
      2lh   & 2.0                 & 2.5  & 20.0\% & 22.42 & 22.42 & 3l1      & 11.5 & 2.9  & 74.8\% & 52.22 & 52.46 \\
      3l2   & 10.2                & 5.2  & 49.0\% & 55.56 & 55.84 & 4l1      & 10.2 & 3.4  & 66.7\% & 37.71 & 37.89 \\
      5l1   & 11.7                & 5.7  & 51.3\% & 29.17 & 29.32 & 6l1      & 10.3 & 7.8  & 24.3\% & 23.73 & 23.86 \\
      8l1   & 13.2                & 14.9 & 11.4\% & 17.26 & 17.36 & 10l1     & 13.3 & 13.5 & 1.5\%  & -     & -     \\
      Si111 & 33.6                & 34.7 & 3.2\%  & -     & -     & Silicene & 11.4 & 11.6 & 1.7\%  & 606.4 & 613.4 \\
    \end{tabular}
  \end{ruledtabular}
\end{table*}

@@

\begin{figure}[b]
  \includegraphics[width=0.48\textwidth]{images/pr_direction}
  \caption{\label{fig:pr_direction} (color online) The participation ratio.}
\end{figure}

@@

\begin{figure}[b]
  \includegraphics[width=0.48\textwidth]{images/gruneisen}
  \caption{\label{fig:gruneisen} (color online)Gruneisen parameters.}
\end{figure}

>>>>

% @Author: YangZhou
% @Date:   2017-06-20 20:27:38
% @Last Modified by:   YangZhou
% @Last Modified time: 2017-10-29 21:07:47
\documentclass[%
 reprint,
 amsmath,amssymb,
 aps,
 prb,
]{revtex4-1}
\preprint{APS/123-QED}
\usepackage{graphicx}% Include figure filesxx
\usepackage{bm}% bold math
\newcommand{\angstrom}{\mbox{\normalfont\AA}}
\begin{document}
\title{Anisotropic in-plane thermal conductivity observed in multilayer silicene}
\author{Yang Zhou${}^{1,3}$}
\author{Chao-Yu Chen${}^{2}$}
\author{Zhi-Xin Guo${}^{2}$}
\email{zxguo08@hotmail.com}
\author{Shi-You Chen${}^{1}$}
\author{Hong-Jun Xiang${}^{1}$}
\author{Xin-Gao Gong${}^{1,3}$}
\email{xggong@fudan.edu.cn}
\affiliation{
  ${}^1$Key Laboratory for Computational Physical Science (Ministry of Education), State Key Laboratory of Surface Physics and Department of Physics, Fudan University, Shanghai 200433, China\\
  ${}^2$Department of Physics, Xiangtan University, Xiangtan 411105, China\\
  ${}^3$Collaborative Innovation Center of Advanced Microstructures, Nanjing 210093, Jiangsu, China
}
\begin{abstract}
  By means of non-equilibrium molecular dynamics simulation, we systematically study the thermal transportation properties of different types of multilayer silicon. It is found that the thermal transport properties of multilayer silicon structures have significant surface effect and size effect in thickness direction. Surface reconstruction affects heat transport very well , the thermal conductivity of bilayer silicon with different reconstruction can reach up to $11.6 W/mK$, and can be as low as $1.2 W/mK$ and the anisotropy can be as high as $57.3\%$.With the increase of the number of layers, the thermal conductivity of the zigzag direction changed little, but the thermal conductivity increased significantly in the armchair direction, and the anisotropy of thermal conductivity decreased which is due to the smaller affection in more layer structure. This work could be helpful in the field of heat management, thermoelectric applications involving silicon and other multilayer nano materials in the future.
  \begin{description}
    \item[Keywords]
          Thermal conductivity, multilayer silicon, surface reconstruction, anisotropy
  \end{description}
\end{abstract}

@@

In this paper, we study the thermal conductivity of multilayer silicon structure by using the Boltzmann transportation equation(BTE) method realized in ShengBTE\cite{Li2014}. Because of the abundant silicon structure model, the phase reconstruction has attracted much attention. In order to well simulate the structures of different phase by BTE, the latest Mod potential based on the large scale parallel and efficient LAMMPS molecular dynamics software package\cite{Parks2007} is chosen\cite{Kumagai2007Development}, which is able to reconstruct the silicon material elastic constants, the melting point and phase transition. Firstly, we use conjugate gradient method to optimize these structures. All structures are shown in FIG.\ref{fig:structures}.

@@

@@

We firstly investigate the effect of surface reconstruction on thermal conductivity. 5 kinds of silicon structures of armchair and zigzag were selected to study. The relationship between the thermal conductivity and the length of bilayer silicon in different directions is shown in FIG.\ref{fig:tc_length_sheng}. the thermal conductivity of 2l1 structure increases with the length the most significantly, followed by the 2l3 structure and 2lr3 structure, while the least significant is the structure of 2l2 and 2lh. In addition, the structure with the thermal conductivity increasing significantly with the length is obviously anisotropy, different from single layer silicon and bulk silicon, who tend to be isotropic. In the aspect of structural, smooth 2l1 is most favorable for heat conduction, while 2l2 structure whose surface is made of a highly symmetrical and highly buckling pentacyclic ring "bird cage" is most unfavorable for thermal conductivity but suitable for thermoelectric materials. And the edges of the two directions are similar in shape, leading to small difference of heat transport.

\begin{figure}[b]
  \includegraphics[width=0.48\textwidth]{images/tc_length_sheng}
  \caption{\label{fig:tc_length_sheng} (color online) a) The thermal conductivity dependence on length for five types of bilayer silicon.b) The dependence on length of thermal conductivity for silicon with variable layers.The scatters are the results of BTE calculations while the lines are fitted with Eq.\ref{eq_nemd}. The letter z/a in the legend mean the transport direction is zigzag/armchair.}
\end{figure}

\begin{figure}[b]
  \includegraphics[width=0.48\textwidth]{images/tc_freq}
  \caption{\label{fig:tc_freq} (color online)  The converged thermal conductivity versus phonon frequency of the structures. }
\end{figure}

@@

\begin{table*}
  \caption{\label{tab:table1}
    The thermal conductivity and anisotropic ratio of different multi-layer silicene.Along with the average heat capacity ($kJ/m^3/K$) of zigzag direction and armchair direction.}
  \begin{ruledtabular}
    \begin{tabular}{ccccccc}
          & Minimal period
          & $\kappa_{z,\infty}$
          & $\kappa_{a,\infty}$
          & $\chi$
          & $Cv_{z}$
          & $Cv_{a}$                                                           \\
      \hline
      2l1 & $1 \times 1$             & 42.10 & 57.92 & 27.31\% & 165.8 & 166.7 \\
      2l2 & $\sqrt{2}\times\sqrt{2}$ & 31.11 & 31.11 & 0    \% & 38.44 & 38.44 \\
      2lh & $2 \times 2$             & 3.311 & 5.624 & 41.13\% & 22.42 & 22.42 \\
      3l1 & $2 \times 1$             & 31.44 & 14.05 & 55.29\% & 52.22 & 52.46 \\
      4l1 & $2 \times 1$             & 20.37 & 6.114 & 69.98\% & 37.71 & 37.89 \\
      5l1 & $2 \times 1$             & 19.33 & 6.419 & 66.78\% & 29.17 & 29.32 \\
      6l1 & $2 \times 1$             & 17.78 & 6.527 & 63.29\% & 23.73 & 23.86 \\
      8l1 & $2 \times 1$             & 17.56 & 7.461 & 57.51\% & 17.26 & 17.36 \\
    \end{tabular}
  \end{ruledtabular}
\end{table*}

@@

@@
